A Critical examination of the ROC curve plot

### 2014-10-13 brb-wip-oct.Rmd
edits

> ROC curve describes possible relationships among the probabilities of the various types of correct and incorrect decisions. Therefore, it plays a central role in optimizing diagnostic strategies

> Conventional ROC curve describes the compromises that can be made between TPF and FPF as a decision threshold is varied. By appropriate choice of the decision threshold, a decision maker or observer can operate at (or near) any desired compromise that lies on the curve.

@@

  - [`ROCR`](http://rocr.bioinf.mpi-sb.mpg.de/) (Encodes cutoff values as color scale along curves)
  - [`pROC`](http://web.expasy.org/pROC/) (Basically standard R plot with CIs)
  - Others for specific estimation methods
  - Roll your own

>>>>

> ROC curve describes possible relationships among the probabilities of the various types of correct and incorrect decisions. Therefore, it plays a central role in optimizing diagnostic strategies
- Lusted, 1971

> Conventional ROC curve describes the compromises that can be made between TPF and FPF as a decision threshold is varied. By appropriate choice of the decision threshold, a decision maker or observer can operate at (or near) any desired compromise that lies on the curve.
- Metz, 1978

@@

  - [`ROCR`](http://rocr.bioinf.mpi-sb.mpg.de/) (Encodes cutoff values as color scale along curve)
  - [`pROC`](http://web.expasy.org/pROC/) (Basically standard R plot with CIs)
  - Others for specific estimation methods
  - Roll your own
